Near Optimal Behavior with Approximate Abstraction

### 2016-02-04 paper/theory_results.tex
Slight theory results shortenings

% Q* Lemma -- lemma 1
We consider an approximate version of the $Q^*$-irrelevance abstraction.

@@

Inspired by the model-irrelevance abstraction, we consider the approximate case. 
\bdefn{$\epM$}
We let $\epM$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
\begin{multline}
\epM(s_1) = \epM(s_2) \rightarrow \\
\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \epsilon \wedge\ \\
\forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \epsilon
\end{multline}
\edefn

>>>>

% Q* Lemma -- lemma 1
We consider an approximate version of \citeauthor{li2006towards}'s $\phi_Q^*$.

@@

Now consider an approximate version of \citeauthor{li2006towards}'s $\phi_{model}$. 
\bdefn{$\epM$}
We let $\epM$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
\begin{multline}
\epM(s_1) = \epM(s_2) \rightarrow \\
\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \epsilon \wedge\ \\
\forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \epsilon
\end{multline}
\edefn
